Pages written in a given year

### 2023-01-12 src/pages.Rmd
Added source to 2000 files

```{r}
write_yaml <- function(page_year) {
  date_line <- paste0("date", ": 20", page_year, "-12-31")
  output_text <- glue('
  ---
  title: "Pages written in 20{page_year}"
  source: new
  date: 20{page_year}-12-31
  categories:
  - Blog post
  tags:
  - Website details
  output: html_document
  ---')
  return(output_text)
}
```

>>>>

```{r}
write_yaml <- function(page_year) {
  century <- ifelse(page_year==99, 19, 20)
  output_text <- glue('
  ---
  title: "Pages written in {century}{page_year}"
  source: new
  date: {century}{page_year}-12-31
  categories:
  - Blog post
  tags:
  - Website details
  output: html_document
  ---')
  return(output_text)
}
```
